---
title: "1.2.1 Build Multivariate VAR Models"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ModelBuildMultivariateVAR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Setup Libraries
```{r setup}
library(tswgewrapped)
```

# Load Data
```{r}
file = system.file("extdata", "USeconomic.csv", package = "tswgewrapped", mustWork = TRUE)
data = read.csv(file, header = TRUE, stringsAsFactors = FALSE, check.names = FALSE)
names(data) = gsub("[(|)]", "", colnames(data))
```
 

# Basic Analysis

## Setup Model Configurations

```{r}
lag.max = 10

models = list("AIC None" = list(select = "aic", trend_type = "none", lag.max = lag.max),
              "AIC Trend"    = list(select = "aic", trend_type = "trend", lag.max = lag.max),
              "AIC Both" = list(select = "aic", trend_type = "both", lag.max = lag.max),
              "BIC None" = list(select = "bic", trend_type = "none", lag.max = lag.max),
              "BIC Trend"    = list(select = "bic", trend_type = "trend", lag.max = lag.max),
              "BIC Both" = list(select = "bic", trend_type = "both", lag.max = lag.max))

var_interest = 'logGNP'
```

## Build Models
```{r}
mdl_build = ModelBuildMultivariateVAR$new(data = data, var_interest = var_interest,
                                          mdl_list = models, verbose = 1)
```

## Summarize the initial build
```{r}
mdl_build$summarize_build()
```

## Get recommendations to prevent overfitting
```{r}
mdl_build$get_recommendations()
```



## Build the recommended models
```{r}
mdl_build$build_recommended_models()
```

## Get the final models
```{r}
# Get only user defined models (subset = 'u')
# Other options are ony recommended models (subset = 'r') or all models (subset = 'a') 
models = mdl_build$get_final_models(subset = 'u')
print(names(models))
```


# Advanced Options

## Adding Seasonality

```{r}
lag.max = 10

models = list("AIC Trend"    = list(select = "aic", trend_type = "trend", season = 3, lag.max = lag.max),
              "BIC Trend"    = list(select = "bic", trend_type = "trend", season = 4, lag.max = lag.max)
              )

var_interest = 'logGNP'
```

### Build Models
```{r}
mdl_build = ModelBuildMultivariateVAR$new(data = data, var_interest = var_interest,
                                          mdl_list = models, verbose = 1)
```

### Summarize the initial build
```{r}
mdl_build$summarize_build()
```

### Get recommendations to prevent overfitting
```{r}
mdl_build$get_recommendations()
```

## Build the recommended models
```{r}
mdl_build$build_recommended_models()
```

## Getting Final Models

```{r}
# Get only recommended model
models = mdl_build$get_final_models(subset = 'r')
print(names(models))
```


```{r}
# Get all models
models = mdl_build$get_final_models(subset = 'a')
print(names(models))
```

