---
title: "ModelCompareUnivariate"
author: "Nikhil Gupta"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ModelCompareUnivariate}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**The objective of this vignette is to show how to use the ModelCompareUnivariate object to compare multiple potential models.**

# Setup Libraries
```{r setup}
library(tswgewrapped)
library(tswge)
```

# Load Data
```{r}
data("airlog")
```
 
# Setup Models tpo be compared 
```{r} 
# Woodward Gray Airline Model
phi_wg = c(-0.36, -0.05, -0.14, -0.11, 0.04, 0.09, -0.02, 0.02, 0.17, 0.03, -0.10, -0.38)
d_wg = 1
s_wg = 12

# Parzen Model
phi_pz = c(0.74, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.38, -0.2812)
s_pz = 12

# Box Model
d_bx = 1
s_bx = 12  
theta_bx =  c(0.40, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0.60, -0.24)

models = list("Woodward Gray Model A" = list(phi = phi_wg, d = d_wg, s = s_wg, vara = 0.001357009, sliding_ase = FALSE),
              "Woodward Gray Model B" = list(phi = phi_wg, d = d_wg, s = s_wg, vara = 0.001357009, sliding_ase = TRUE),
              "Parzen Model A" = list(phi = phi_pz, s = s_pz, vara = 0.002933592, sliding_ase = FALSE),
              "Parzen Model B" = list(phi = phi_pz, s = s_pz, vara = 0.002933592, sliding_ase = TRUE),
              "Box Model A" = list(theta = theta_bx, d = d_bx, s = s_bx, vara = 0.001391604, sliding_ase = FALSE),
              "Box Model B" = list(theta = theta_bx, d = d_bx, s = s_bx, vara = 0.001391604, sliding_ase = TRUE)
              )
```

# Initialize the ModelCompareUnivariate object
```{r}
#### With n_step.ahead = TRUE (Default)              
mdl_compare = ModelCompareUnivariate$new(x = airlog, mdl_list = models,
                                         n.ahead = 36, batch_size = 72)

```

# Compare the models

## Plot Multiple realizations
```{r}
mdl_compare$plot_multiple_realizations(n.realizations = 4, seed = 100)
```

## Compare Histogram of ASE values
```{r}
mdl_compare$plot_histogram_ases()
```

## Statistically Compare the models
```{r}
mdl_compare$statistical_compare()  
```

## Plot and compare the forecasrs per batch
```{r}
mdl_compare$plot_forecasts(only_sliding = TRUE)
```

## Raw Data and Metrics
```{r}
ASEs = mdl_compare$get_tabular_metrics(ases = TRUE)
print(ASEs)
```

```{r}
forecasts = mdl_compare$get_tabular_metrics(ases = FALSE)
print(forecasts)
```